Supplementary Material

### 2019-01-10 analyses/reproduce_analyses.Rmd
reduced fig and font size for Platygaster selection (Fig. 4)

eggptoid_selection_plot <- eggptoid_plot_df %>%
  ggplot(., aes(x=sc.sqrt.Pref, y=fitness_difference, group=ID, alpha=ID_group, size=ID_group)) +
  geom_line(color=cbPalette[5]) +
  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
  xlab("Gall midge preference (SDs)") + 
  ylab(expression(paste(Delta," egg parasitoid survival (complex - simple)"))) +
  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
  geom_hline(yintercept=0, linetype="dotted")

eggptoid_selection_plot
save_plot(filename = "selection_on_Platygaster.pdf", plot = eggptoid_selection_plot, base_height = 6)
```

@@

# Size x Clutch
AF_plot_Diam.Clutch <- RF_Diam.Clutch$absolute_fitness %>% 
  ggplot(., aes(x=sc.Diam, y=sc.log.Clutch)) +
  geom_raster(aes(fill=average)) +
  facet_wrap(~Foodweb) +
  xlab("Gall diameter (SDs)") +
  ylab("Clutch size (SDs)") +
  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
  theme(strip.background = element_blank(),
        strip.text.x=element_text(margin=margin(b=4)))

# Size x Preference
AF_plot_Diam.Pref <- RF_Diam.Pref$absolute_fitness %>% 
  ggplot(., aes(x=sc.Diam, y=sc.sqrt.Pref)) +
  geom_raster(aes(fill=average)) +
  facet_wrap(~Foodweb) +
  xlab("Chamber diameter (SDs)") +
  ylab("Oviposition preference (SDs)") +
  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
  theme(strip.background = element_blank(),
        strip.text.x=element_text(margin=margin(b=4)))

@@

# Set contour breaks
breaks <- predict(foodweb_model, newdata=data.frame(sc.Diam = c(0,0), sc.log.Clutch = c(0,0), sc.sqrt.Pref = c(0,0), Foodweb = c("Complex","Simple")), type="response", re.form=~0)

# Format plots
AF_landscape_plots <- plot_grid(
  AF_plot_Diam.Clutch + theme(legend.position = "none", 
                              axis.title.x = element_blank(),
                             axis.text.x = element_blank()) +
    stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") + # mean(RF_Diam.Pref$absolute_fitness$average)
    geom_segment(data = gradients_Diam.Clutch, 
                 aes(x = sc.Diam, y = sc.log.Clutch, xend = xend, yend = yend), 
                 arrow = arrow(length = unit(0.03, "npc"))),
  AF_plot_Clutch.Pref + theme(legend.position = "none", 
                              axis.title.y = element_blank(),
                              axis.text.y = element_blank()) + xlab("Preference (SDs)") +
    stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") +
    geom_segment(data = gradients_Clutch.Pref, 
                 aes(x = sc.sqrt.Pref, y = sc.log.Clutch, xend = xend, yend = yend), 
                 arrow = arrow(length = unit(0.03, "npc"))), 
  AF_plot_Diam.Pref + theme(legend.position = "none") + ylab("Preference (SDs)") +
    stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") +
    geom_segment(data = gradients_Diam.Pref, 
                 aes(x = sc.Diam, y = sc.sqrt.Pref, xend = xend, yend = yend), 
                 arrow = arrow(length = unit(0.03, "npc"))), 
  nrow=2, align="hv", labels = "AUTO")

@@

>>>>

eggptoid_selection_plot <- eggptoid_plot_df %>%
  ggplot(., aes(x=sc.sqrt.Pref, y=fitness_difference, group=ID, alpha=ID_group, size=ID_group)) +
  geom_line(color=cbPalette[5]) +
  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
  xlab("Gall midge preference (SDs)") + 
  ylab(expression(paste(Delta," egg parasitoid survival (complex - simple)"))) +
  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
  geom_hline(yintercept=0, linetype="dotted") +
  theme_cowplot(font_size = 12)

eggptoid_selection_plot
save_plot(filename = "selection_on_Platygaster.pdf", plot = eggptoid_selection_plot, base_height = 4) # base_height = 6
```

@@

# Set contour breaks
breaks <- predict(foodweb_model, newdata=data.frame(sc.Diam = c(0,0), sc.log.Clutch = c(0,0), sc.sqrt.Pref = c(0,0), Foodweb = c("Complex","Simple")), type="response", re.form=~0)
names(breaks) <- c("Complex","Simple")

# Size x Clutch
AF_plot_Diam.Clutch <- RF_Diam.Clutch$absolute_fitness %>% 
  filter(Foodweb == "Complex") %>%
  ggplot(., aes(x=sc.Diam, y=sc.log.Clutch)) +
  geom_raster(aes(fill=average)) +
  stat_contour(aes(z = average), breaks = breaks["Complex"], linetype = "dotted", color = "black") +
  geom_raster(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Simple"), aes(fill=average)) +
  stat_contour(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
  facet_wrap(~Foodweb) +
  xlab("Gall diameter (SDs)") +
  ylab("Clutch size (SDs)") +
  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
  theme(strip.background = element_blank(),
        strip.text.x=element_text(margin=margin(b=4)))

# Size x Preference
AF_plot_Diam.Pref <- RF_Diam.Pref$absolute_fitness %>% 
  filter(Foodweb == "Complex") %>%
  ggplot(., aes(x=sc.Diam, y=sc.sqrt.Pref)) +
  geom_raster(aes(fill=average)) +
  stat_contour(aes(z = average), breaks = breaks["Complex"], linetype = "dotted", color = "black") +
  geom_raster(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Simple"), aes(fill=average)) +
  stat_contour(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
  facet_wrap(~Foodweb) +
  xlab("Chamber diameter (SDs)") +
  ylab("Oviposition preference (SDs)") +
  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
  theme(strip.background = element_blank(),
        strip.text.x=element_text(margin=margin(b=4)))

# Clutch x Preference
AF_plot_Clutch.Pref <- RF_Clutch.Pref$absolute_fitness %>%
  filter(Foodweb == "Complex") %>%
  ggplot(., aes(x=sc.sqrt.Pref, y=sc.log.Clutch)) +
  geom_raster(aes(fill=average)) +
  stat_contour(aes(z = average), breaks = breaks["Complex"], linetype = "dotted", color = "black") +
  geom_raster(data = filter(RF_Clutch.Pref$absolute_fitness, Foodweb == "Simple"), aes(fill=average)) +
  stat_contour(data = filter(RF_Clutch.Pref$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
  facet_wrap(~Foodweb) +
  xlab("Oviposition preference (SDs)") +
  ylab("Clutch size (SDs)") +
  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
  theme(strip.background = element_blank(),
        strip.text.x=element_text(margin=margin(b=4)))

@@

# Format plots
AF_landscape_plots <- plot_grid(
  AF_plot_Diam.Clutch + theme(legend.position = "none", 
                              axis.title.x = element_blank(),
                             axis.text.x = element_blank()) +
    #stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") + # mean(RF_Diam.Pref$absolute_fitness$average)
    geom_segment(data = gradients_Diam.Clutch, 
                 aes(x = sc.Diam, y = sc.log.Clutch, xend = xend, yend = yend), 
                 arrow = arrow(length = unit(0.03, "npc"))),
  AF_plot_Clutch.Pref + theme(legend.position = "none", 
                              axis.title.y = element_blank(),
                              axis.text.y = element_blank()) + xlab("Preference (SDs)") +
    #stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") +
    geom_segment(data = gradients_Clutch.Pref, 
                 aes(x = sc.sqrt.Pref, y = sc.log.Clutch, xend = xend, yend = yend), 
                 arrow = arrow(length = unit(0.03, "npc"))), 
  AF_plot_Diam.Pref + theme(legend.position = "none") + ylab("Preference (SDs)") +
    #stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") +
    geom_segment(data = gradients_Diam.Pref, 
                 aes(x = sc.Diam, y = sc.sqrt.Pref, xend = xend, yend = yend), 
                 arrow = arrow(length = unit(0.03, "npc"))), 
  nrow=2, align="hv", labels = "AUTO")

@@

```{r }
# Plot helpers
AF_range <- bind_rows(RF_Clutch.Pref$absolute_fitness, RF_Diam.Clutch$absolute_fitness, RF_Diam.Pref$absolute_fitness) %>%
  summarise(min = min(average), max = max(average))

# Set contour breaks
breaks <- predict(foodweb_model, newdata=data.frame(sc.Diam = c(0,0), sc.log.Clutch = c(0,0), sc.sqrt.Pref = c(0,0), Foodweb = c("Complex","Simple")), type="response", re.form=~0)
names(breaks) <- c("Complex","Simple")

# Size x Clutch
AF_plot_Diam.Clutch <- RF_Diam.Clutch$absolute_fitness %>%
  filter(Foodweb == "Complex") %>%
  ggplot(., aes(x=sc.Diam, y=sc.log.Clutch)) +
  geom_raster(aes(fill=average)) +
  stat_contour(aes(z = average), breaks = breaks["Complex"], linetype = "dotted", color = "black") +
  geom_raster(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Simple"), aes(fill=average)) +
  stat_contour(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
  facet_wrap(~Foodweb) +
  xlab("Gall diameter (SDs)") +
  ylab("Clutch size (SDs)") +
  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
  theme(strip.background = element_blank(),
        strip.text.x=element_text(margin=margin(b=4)))

# Size x Preference
AF_plot_Diam.Pref <- RF_Diam.Pref$absolute_fitness %>% 
  #filter(Foodweb == "Complex") %>%
  ggplot(., aes(x=sc.Diam, y=sc.sqrt.Pref)) +
  geom_raster(aes(fill=average)) +
  #stat_contour(aes(z = average), breaks = breaks["Complex"], linetype = "dotted", color = "black") +
  #geom_raster(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Simple"), aes(fill=average)) +
  #stat_contour(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
  facet_wrap(~Foodweb) +
  xlab("Chamber diameter (SDs)") +
  ylab("Oviposition preference (SDs)") +
  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
  theme(strip.background = element_blank(),
        strip.text.x=element_text(margin=margin(b=4)))

Remove 2nd contour line

```{r Figure-Multivariate-Landscapes-2, echo=FALSE, fig.cap="Fitness landscapes of gall traits in complex vs. simple food webs. Each panel corresponds to a different combination of traits: clutch size and gall diameter (A); clutch size and Oviposition preference (B); Oviposition preference and gall diameter (C). Note that traits for all plots range 1 SD below and above the mean (=0)."}

# Format plots
AF_landscape_plots <- plot_grid(
  AF_plot_Diam.Clutch + theme(legend.position = "none", 
                              axis.title.x = element_blank(),
                             axis.text.x = element_blank()) +
   # stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") + # mean(RF_Diam.Pref$absolute_fitness$average)
    geom_segment(data = gradients_Diam.Clutch, 
                 aes(x = sc.Diam, y = sc.log.Clutch, xend = xend, yend = yend), 
                 arrow = arrow(length = unit(0.03, "npc"))),
  AF_plot_Clutch.Pref + theme(legend.position = "none", 
                              axis.title.y = element_blank(),
                              axis.text.y = element_blank()) + xlab("Preference (SDs)") +
    stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") +
    geom_segment(data = gradients_Clutch.Pref, 
                 aes(x = sc.sqrt.Pref, y = sc.log.Clutch, xend = xend, yend = yend), 
                 arrow = arrow(length = unit(0.03, "npc"))), 
  AF_plot_Diam.Pref + theme(legend.position = "none") + ylab("Preference (SDs)") +
    #stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") +
    geom_segment(data = gradients_Diam.Pref, 
                 aes(x = sc.Diam, y = sc.sqrt.Pref, xend = xend, yend = yend), 
                 arrow = arrow(length = unit(0.03, "npc"))), 
  nrow=2, align="hv", labels = "AUTO")

AF_landscape_2d <- ggdraw(AF_landscape_plots) + draw_grob(AF_landscape_legend, x = 0.7, y=-0.2)
AF_landscape_2d
save_plot(filename = "MV_landscapes_2.pdf", plot = AF_landscape_2d, base_width=8, base_height = 6)
```
